---
title: "rater_comparison_overall"
output: html_document
---

```{r install_packages, include=FALSE}

# install rel from archive
library(devtools)
install_url('https://cran.r-project.org/src/contrib/Archive/rel/rel_1.4.2.tar.gz')

```

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(rel)
library(ggplot2)
library(reshape)


# Set up settings and consts
filename = 'adult_example_etdset.csv'

# Read collated data file
data_full = read_csv(filename)

# Replace right value - from -1 to 2 for CK analysis
data_full$agazeraw[data_full$agazeraw == -1] = 2
data_full$algazeraw[data_full$algazeraw == -1] = 2
data_full$argazeraw[data_full$argazeraw == -1] = 2

# Replace right value - from -1 to 2 for CK analysis
data_full$sgazeraw[data_full$sgazeraw == -1] = 2
data_full$slgazeraw[data_full$slgazeraw == -1] = 2
data_full$srgazeraw[data_full$srgazeraw == -1] = 2

# split data by ppt
data_split = split(data_full, f = as.factor(data_full$PID))
# 
#split into static and pursuit
data_dynamic = data_full %>%
  filter(h_movement=="moving")
# 
data_dynamic_split = data_dynamic %>%
  split(f = as.factor(.$PID))
# 
data_static = data_full %>%
  filter(h_movement!="moving")
#
data_static_split = data_static %>%
  split(f = as.factor(.$PID))

```





# Static frames for Overall data
## Aggregate scores

```{r}


# run CK on static frames
CK_data = select(data_static, agazeraw, sgazeraw)
static_CK_o = ckap(data = CK_data, weight = 'unweighted')
print(static_CK_o)

```

## Aggregate confusion matrix
```{r}
print(table(CK_data))
```

## Cohen-Kappa by participant
```{r}
# Run split CK on static
static_CK_o_split = NULL
output = lapply(data_static_split, function(i){
  CK_data = select(i, sgazeraw, agazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
static_CK_o_split = do.call(rbind.data.frame, output)
print(static_CK_o_split)

```



# Static frames for right eye
## Aggregate scores

```{r}

# run CK on static 
CK_data = select(data_static, argazeraw, srgazeraw)
static_CK_r = ckap(data = CK_data, weight = 'unweighted')
print(static_CK_r)

```

## Aggregate confusion matrix
```{r}
print(table(CK_data))
```

## Cohen-Kappa by participant
```{r}
# Run split CK on static
static_CK_r_split = NULL
output = lapply(data_static_split, function(i){
  CK_data = select(i, argazeraw, srgazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
static_CK_r_split = do.call(rbind.data.frame, output)
print(static_CK_r_split)

```



# Static frames for left eye
## Aggregate scores

```{r}

# run CK on static 
CK_data = select(data_static, algazeraw, slgazeraw)
static_CK_l = ckap(data = CK_data, weight = 'unweighted')
print(static_CK_l)

```

## Aggregate confusion matrix
```{r}
print(table(CK_data))
```

## Cohen-Kappa by participant
```{r}
# Run split CK on static
static_CK_l_split = NULL
output = lapply(data_static_split, function(i){
  CK_data = select(i, algazeraw, slgazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
static_CK_l_split = do.call(rbind.data.frame, output)
print(static_CK_l_split)

```


# Combined plots for CK scores accross all participants

```{r}

replace_pid = T

if (replace_pid){
  PID_names = sprintf('%0.3d', 1:nrow(static_CK_l_split))
  static_CK_l_split = cbind(static_CK_l_split,PID_names)

} else {
  PID_names = rownames(static_CK_l_split)
}

plot_fname_static = 'plots/adult_static_CK_plot.png'

static_plots = data.frame(Name = PID_names, static_CK_o_split$est, static_CK_l_split$est, static_CK_r_split$est) 

static_plots_se = data.frame(Name = PID_names, static_CK_o_split$se, static_CK_l_split$se, static_CK_r_split$se)


names(static_plots)[2] <- "Overall"
names(static_plots)[3] <- "Left"
names(static_plots)[4] <- "Right"

names(static_plots_se)[2] <- "Overall"
names(static_plots_se)[3] <- "Left"
names(static_plots_se)[4] <- "Right"

df = melt(static_plots, id.vars = "Name")
df_se = melt(static_plots_se, id.vars = "Name")
names(df_se)[3] <- 'error'

df = merge(df, df_se)

ggplot(df, aes(x = Name, y = value, color = factor(variable))) +
  geom_pointrange(aes(ymin=value-error, ymax=value+error), position = position_dodge(width = 0.75), size=0.3) +
  scale_y_continuous(limits = c(-0.2, 1.1),  breaks = seq(0, 1, by = 0.2)) +
  # ylim(0,1.01) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  geom_hline(yintercept=0.61, linetype="dashed", color = "black")+
  labs(y="Cohen's kappa score", x = "Participant ID.")

ggsave(plot_fname_static)
```





# dynamic frames for Overall data
## Aggregate scores

```{r}

# run CK on dynamic 
CK_data = select(data_dynamic, agazeraw, sgazeraw)
dynamic_CK_o = ckap(data = CK_data, weight = 'unweighted')
print(dynamic_CK_o)

```

## Aggregate confusion matrix
```{r}
print(table(CK_data))
```

## Cohen-Kappa by participant
```{r}
# Run split CK on dynamic
dynamic_CK_o_split = NULL
output = lapply(data_dynamic_split, function(i){
  CK_data = select(i, sgazeraw, agazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
dynamic_CK_o_split = do.call(rbind.data.frame, output)
print(dynamic_CK_o_split)

```



# dynamic frames for right eye
## Aggregate scores

```{r}

# run CK on dynamic 
CK_data = select(data_dynamic, argazeraw, srgazeraw)
dynamic_CK_r = ckap(data = CK_data, weight = 'unweighted')
print(dynamic_CK_r)

```

## Aggregate confusion matrix
```{r}
print(table(CK_data))
```

## Cohen-Kappa by participant
```{r}
# Run split CK on dynamic
dynamic_CK_r_split = NULL
output = lapply(data_dynamic_split, function(i){
  CK_data = select(i, argazeraw, srgazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
dynamic_CK_r_split = do.call(rbind.data.frame, output)
print(dynamic_CK_r_split)

```



# dynamic frames for left eye
## Aggregate scores

```{r}

# run CK on dynamic 
CK_data = select(data_dynamic, algazeraw, slgazeraw)
dynamic_CK_l = ckap(data = CK_data, weight = 'unweighted')
print(dynamic_CK_l)

```

## Aggregate confusion matrix
```{r}
print(table(CK_data))
```

## Cohen-Kappa by participant
```{r}
# Run split CK on dynamic
dynamic_CK_l_split = NULL
output = lapply(data_dynamic_split, function(i){
  CK_data = select(i, algazeraw, slgazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
dynamic_CK_l_split = do.call(rbind.data.frame, output)
print(dynamic_CK_l_split)

```


# Combined plots for CK scores accross all participants

```{r}


replace_pid = T

if (replace_pid){
  PID_names = sprintf('%0.3d', 1:nrow(dynamic_CK_l_split))
  dynamic_CK_l_split = cbind(dynamic_CK_l_split,PID_names)

} else {
  PID_names = rownames(dynamic_CK_l_split)
}

plot_fname_dynamic = 'plots/adult_dynamic_CK_plot.png'

dynamic_plots = data.frame(Name = PID_names, dynamic_CK_o_split$est, dynamic_CK_l_split$est, dynamic_CK_r_split$est) 

dynamic_plots_se = data.frame(Name = PID_names, dynamic_CK_o_split$se, dynamic_CK_l_split$se, dynamic_CK_r_split$se)


names(dynamic_plots)[2] <- "Overall"
names(dynamic_plots)[3] <- "Left"
names(dynamic_plots)[4] <- "Right"

names(dynamic_plots_se)[2] <- "Overall"
names(dynamic_plots_se)[3] <- "Left"
names(dynamic_plots_se)[4] <- "Right"

df = melt(dynamic_plots, id.vars = "Name")
df_se = melt(dynamic_plots_se, id.vars = "Name")
names(df_se)[3] <- 'error'

df = merge(df, df_se)

ggplot(df, aes(x = Name, y = value, color = factor(variable))) +
  geom_pointrange(aes(ymin=value-error, ymax=value+error), position = position_dodge(width = 0.75), size=0.3) +
  scale_y_continuous(limits = c(-0.2
                                , 1),  breaks = seq(0, 1, by = 0.2)) +
  # ylim(0,1.01) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  geom_hline(yintercept=0.61, linetype="dashed", color = "black")+
  labs(y="Cohen's kappa score", x = "Participant ID.")

ggsave(plot_fname_dynamic)
```

# Combined plot for smoot pursuit subplots
## Aggregate scores
```{r, echo=FALSE}


replace_pid = T

if (replace_pid){
  PID_names = sprintf('%0.3d', 1:nrow(dynamic_CK_l_split))
  dynamic_CK_l_split = cbind(dynamic_CK_l_split,PID_names)

} else {
  PID_names = rownames(dynamic_CK_l_split)
}

plot_fname = 'plots/adult_dynamic_comparison_CK_plot.png'

#select .5 - 1 % excursion and static frames
temp_data_dynamic_0_0.5 = data_full[which((data_full$h_location > 0 & data_full$h_location < 0.5) | (data_full$h_location < 0 & data_full$h_location > -0.5)),]

temp_data_dynamic = temp_data_dynamic_0_0.5 %>% 
  split(f = as.factor(.$PID))
temp_dynamic_0_0.5 = NULL
output = lapply(temp_data_dynamic, function(i){
  CK_data = select(i, sgazeraw, agazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
temp_dynamic_0_0.5 = do.call(rbind.data.frame, output)


temp_data_dynamic_0.5_1 = data_full[which((data_full$h_location > 0.5 & data_full$h_location < 1) | (data_full$h_location < -0.5 & data_full$h_location > -1)),]

temp_data_dynamic = temp_data_dynamic_0.5_1 %>% 
  split(f = as.factor(.$PID))
temp_dynamic_0.5_1 = NULL
output = lapply(temp_data_dynamic, function(i){
  CK_data = select(i, sgazeraw, agazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
temp_dynamic_0.5_1 = do.call(rbind.data.frame, output)

temp_data_dynamic_0.75_1 = data_full[which((data_full$h_location > 0.75 & data_full$h_location < 1) | (data_full$h_location < -0.75 & data_full$h_location > -1)),]

temp_data_dynamic = temp_data_dynamic_0.75_1 %>% 
  split(f = as.factor(.$PID))
temp_dynamic_0.75_1 = NULL
output = lapply(temp_data_dynamic, function(i){
  CK_data = select(i, sgazeraw, agazeraw)
  my_list = ckap(data = CK_data, weight = 'unweighted') #})
  my_list[names(my_list) %in% c("method", "call",  "mat", "weight", "data") == FALSE]})
temp_dynamic_0.75_1 = do.call(rbind.data.frame, output)


dynamic_plots = data.frame(Name = PID_names, temp_dynamic_0_0.5$est, temp_dynamic_0.5_1$est, temp_dynamic_0.75_1$est)

dynamic_plots_se = data.frame(Name = PID_names, temp_dynamic_0_0.5$se, temp_dynamic_0.5_1$se, temp_dynamic_0.75_1$se)



names(dynamic_plots)[2] <- "0 - 0.5"
names(dynamic_plots)[3] <- "0.5 - 1"
names(dynamic_plots)[4] <- "0.75 - 1"


names(dynamic_plots_se)[2] <- "0 - 0.5"
names(dynamic_plots_se)[3] <- "0.5 - 1"
names(dynamic_plots_se)[4] <- "0.75 - 1"


df = melt(dynamic_plots, id.vars = "Name")
df_se = melt(dynamic_plots_se, id.vars = "Name")
names(df_se)[3] <- 'error'

df = merge(df, df_se)

ggplot(df, aes(x = Name, y = value, color = factor(variable))) +
  geom_pointrange(aes(ymin=value-error, ymax=value+error), position = position_dodge(width = 0.75), size=0.3) +
  scale_y_continuous(limits = c(-0.4, 1),  breaks = seq(-0.3, 1, by = 0.2)) +
  # ylim(0,1.01) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  geom_hline(yintercept=0.61, linetype="dashed", color = "black")+
  geom_hline(yintercept=0, color = "black") + 
  labs(y="Cohen's kappa score", x = "Participant ID.")

ggsave(plot_fname)
```



# Pursuit frames with excursion between 0 - 0.5 
## Aggregate scores
```{r, echo=FALSE}



# run CK on dynamic 
CK_data = select(temp_data_dynamic_0_0.5, agazeraw, sgazeraw)
dynamic_CK_o = ckap(data = CK_data, weight = 'unweighted')
print(dynamic_CK_o)

```


```{r, echo=FALSE}
print(table(CK_data))

```


# Pursuit frames with excursion between 0.5 - 1
## Aggregate scores
```{r, echo=FALSE}


# run CK on dynamic 
CK_data = select(temp_data_dynamic_0.5_1, agazeraw, sgazeraw)
dynamic_CK_o = ckap(data = CK_data, weight = 'unweighted')
print(dynamic_CK_o)


```


```{r, echo=FALSE}
print(table(CK_data))

```



# Pursuit frames with excursion between 0.75 - 1 
## Aggregate scores
```{r, echo=FALSE}


# run CK on dynamic 
CK_data = select(temp_data_dynamic_0.75_1, agazeraw, sgazeraw)
dynamic_CK_o = ckap(data = CK_data, weight = 'unweighted')
print(dynamic_CK_o)

```


```{r, echo=FALSE}
print(table(CK_data))

```
